### 2019-04-02 Model.tex
sections 1-3 fixes

Both our method and the comparison sate-of-the-art RNN takes more time than a vanilla-RNN, by a factor of $K$, because there are $K$ permutations for each datapoint. Our proposed method is slower than the RNN baseline by a factor of 1.5 (approximatively) because each epoch requires one more forward pass.

>>>>

Both our method and the comparison sate-of-the-art (Vinyals-RNN) take more time than a vanilla-RNN, by a factor of $K$, because there are $K$ permutations considered for each datapoint. Our proposed method is about as fast as the Vinyals-RNN methods, except for the Vinyals-RNN-uniform which is a bit faster (by a factor of 1.5) because its epochs do not run the additional forward pass.
